---
title: "Study2_moderation_markdown"
author: "Faye Sanders"
date: "2026-04-17"
output: html_document
---

```{r setup, include=FALSE}

# Load required libraries
library(mice)
library(dplyr)
library(lavaan)
library(purrr)
library(ggplot2)
library(ggcorrplot)
library(gt)
library(tidyr)

# -----------------------------
# Step 1: Load and Prepare Data
# -----------------------------
imp_data <- readRDS("...rds")

built_env_vars <- c(
  'building_density_age28mum',
  'connectivity_density_age28mum',
  'facility_richness_age28mum',
  'greenspace_age28mum',
  'pop_density_age28mum',
  'walkability_age28mum'
)

imp_list <- complete(imp_data, action = "all")

# -----------------------------
# Step 2: CFA + Extract Scores
# -----------------------------
cfa_model <- '
  BuiltEnv =~ building_density_age28mum +
              connectivity_density_age28mum +
              facility_richness_age28mum +
              greenspace_age28mum +
              pop_density_age28mum +
              walkability_age28mum
'

imp_list_with_scores <- lapply(imp_list, function(df) {

  df[built_env_vars] <- scale(df[built_env_vars])
  fit <- cfa(cfa_model, data = df, estimator = "MLR")
  df$BuiltEnv <- lavPredict(fit)[, "BuiltEnv"]

  # Centred variables
  df$BuiltEnv_c <- scale(df$BuiltEnv, center = TRUE, scale = FALSE)[, 1]
  df$active_travel_age30mum_c <- scale(df$active_travel_age30mum, center = TRUE, scale = FALSE)[, 1]
  df$age_at_birth_mums_c <- scale(df$age_at_birth_mums, center = TRUE, scale = FALSE)[, 1]
  df$contextual_age28mum_c <- scale(df$contextual_age28mum, center = TRUE, scale = FALSE)[, 1]
  df$physical_activity_age28mum_c <- scale(df$physical_activity_age28mum, center = TRUE, scale = FALSE)[, 1]
  df$depression_at_age28mum_c <- scale(df$depression_at_age28mum, center = TRUE, scale = FALSE)[, 1]
  df$familial_depressive_history_c <- scale(df$familial_depressive_history, center = TRUE, scale = FALSE)[, 1]
  df$smoking_age28mum_c <- scale(df$smoking_age28mum, center = TRUE, scale = FALSE)[, 1]

  # Standardised variables for regression estimates
  df$BuiltEnv_z <- scale(df$BuiltEnv)[, 1]
  df$active_travel_age30mum_z <- scale(df$active_travel_age30mum)[, 1]
  df$depression_at_age32mum_z <- scale(df$depression_at_age32mum)[, 1]
  df$age_at_birth_mums_z <- scale(df$age_at_birth_mums)[, 1]
  df$familial_depressive_history_z <- scale(df$familial_depressive_history)[, 1]
  df$contextual_age28mum_z <- scale(df$contextual_age28mum)[, 1]
  df$physical_activity_age28mum_z <- scale(df$physical_activity_age28mum)[, 1]
  df$depression_at_age28mum_z <- scale(df$depression_at_age28mum)[, 1]
  df$smoking_age28mum_z <- scale(df$smoking_age28mum)[, 1]

  return(df)
})


# -----------------------------
# Step 3: Combine & Convert to mids
# -----------------------------
imp_data_long <- bind_rows(imp_list_with_scores, .id = ".imp")
imp_data_long$.imp <- as.integer(imp_data_long$.imp) - 1
imp_data_long <- as.mids(imp_data_long)

# -----------------------------
# Step 4: Moderation Regression
# -----------------------------
# with covariates
moderation_model <- with(imp_data_long, lm(
  depression_at_age32mum ~ active_travel_age30mum_c * BuiltEnv_c +
    age_at_birth_mums_c +
    familial_depressive_history_c +
    contextual_age28mum_c +
    physical_activity_age28mum_c +
    depression_at_age28mum_c +
    smoking_age28mum_c
))

# without covariates
moderation_model2 <- with(imp_data_long, lm(
  depression_at_age32mum ~ active_travel_age30mum_c * BuiltEnv_c
))

# Standardised adjusted model
moderation_model_std <- with(imp_data_long, lm(
  depression_at_age32mum_z ~ active_travel_age30mum_z * BuiltEnv_z +
    age_at_birth_mums_z +
    familial_depressive_history_z +
    contextual_age28mum_z +
    physical_activity_age28mum_z +
    depression_at_age28mum_z +
    smoking_age28mum_z
))

# Standardised unadjusted model
moderation_model2_std <- with(imp_data_long, lm(
  depression_at_age32mum_z ~ active_travel_age30mum_z * BuiltEnv_z
))

# sensitivity analysis set up

sensitivity_data <- readRDS("...rds")

sensitivity_list <- complete(sensitivity_data, action = "all")

# -----------------------------
# Step 2: CFA + Extract Scores
# -----------------------------

sensitivity_list_with_scores <- lapply(sensitivity_list, function(df) {

  df[built_env_vars] <- scale(df[built_env_vars])
  fit <- cfa(cfa_model, data = df, estimator = "MLR")
  df$BuiltEnv <- lavPredict(fit)[, "BuiltEnv"]

  # Existing centred variables
  df$BuiltEnv_c <- scale(df$BuiltEnv, center = TRUE, scale = FALSE)[, 1]
  df$active_travel_age30mum_c <- scale(df$active_travel_age30mum, center = TRUE, scale = FALSE)[, 1]
  df$age_at_birth_mums_c <- scale(df$age_at_birth_mums, center = TRUE, scale = FALSE)[, 1]
  df$contextual_age28mum_c <- scale(df$contextual_age28mum, center = TRUE, scale = FALSE)[, 1]
  df$physical_activity_age28mum_c <- scale(df$physical_activity_age28mum, center = TRUE, scale = FALSE)[, 1]
  df$depression_at_age28mum_c <- scale(df$depression_at_age28mum, center = TRUE, scale = FALSE)[, 1]
  df$familial_depressive_history_c <- scale(df$familial_depressive_history, center = TRUE, scale = FALSE)[, 1]
  df$smoking_age28mum_c <- scale(df$smoking_age28mum, center = TRUE, scale = FALSE)[, 1]

  # NEW: standardised variables
  df$BuiltEnv_z <- scale(df$BuiltEnv)[, 1]
  df$active_travel_age30mum_z <- scale(df$active_travel_age30mum)[, 1]
  df$depression_at_age32mum_z <- scale(df$depression_at_age32mum)[, 1]
  df$age_at_birth_mums_z <- scale(df$age_at_birth_mums)[, 1]
  df$familial_depressive_history_z <- scale(df$familial_depressive_history)[, 1]
  df$contextual_age28mum_z <- scale(df$contextual_age28mum)[, 1]
  df$physical_activity_age28mum_z <- scale(df$physical_activity_age28mum)[, 1]
  df$depression_at_age28mum_z <- scale(df$depression_at_age28mum)[, 1]
  df$smoking_age28mum_z <- scale(df$smoking_age28mum)[, 1]

  return(df)
})


# -----------------------------
# Step 3: Combine & Convert to mids
# -----------------------------
sensitivity_data_long <- bind_rows(sensitivity_list_with_scores, .id = ".imp")
sensitivity_data_long$.imp <- as.integer(sensitivity_data_long$.imp) - 1
sensitivity_data_long <- as.mids(sensitivity_data_long)

# -----------------------------
# Step 4: Moderation Regression
# -----------------------------
# with covariates
sensitivity_model <- with(sensitivity_data_long, lm(
  depression_at_age32mum ~ active_travel_age30mum_c * BuiltEnv_c +
    age_at_birth_mums_c +
    familial_depressive_history_c +
    contextual_age28mum_c +
    physical_activity_age28mum_c +
    depression_at_age28mum_c +
    smoking_age28mum_c
))


# without covariates
sensitivity_model2 <- with(sensitivity_data_long, lm(
  depression_at_age32mum ~ active_travel_age30mum_c * BuiltEnv_c
))

sensitivity_model_std <- with(sensitivity_data_long, lm(
  depression_at_age32mum_z ~ active_travel_age30mum_z * BuiltEnv_z +
    age_at_birth_mums_z +
    familial_depressive_history_z +
    contextual_age28mum_z +
    physical_activity_age28mum_z +
    depression_at_age28mum_z +
    smoking_age28mum_z
))

sensitivity_model2_std <- with(sensitivity_data_long, lm(
  depression_at_age32mum_z ~ active_travel_age30mum_z * BuiltEnv_z
))

#plots set up
# plots set up

# Step 1: Extract pooled coefficients
pooled_coefs <- summary(pool(moderation_model))
pooled_coefs_sens <- summary(pool(sensitivity_model))

# Step 2: Define levels for BuiltEnv and active travel
builtenv_vals <- c(-1, 0, 1)
active_travel_vals <- seq(from = -2, to = 2, length.out = 50)

# Step 3: Create prediction dataframes
pred_grid <- expand.grid(
  active_travel_age30mum_c = active_travel_vals,
  BuiltEnv_c = builtenv_vals
)

pred_grid_sens <- expand.grid(
  active_travel_age30mum_c = active_travel_vals,
  BuiltEnv_c = builtenv_vals
)

# Step 4: Set covariates to their means
covariates_means <- imp_list_with_scores[[1]] %>%
  summarise(
    age_at_birth_mums_c = mean(age_at_birth_mums_c, na.rm = TRUE),
    familial_depressive_history_c = mean(familial_depressive_history_c, na.rm = TRUE),
    contextual_age28mum_c = mean(contextual_age28mum_c, na.rm = TRUE),
    depression_at_age28mum_c = mean(depression_at_age28mum_c, na.rm = TRUE),
    physical_activity_age28mum_c = mean(physical_activity_age28mum_c, na.rm = TRUE),
    smoking_age28mum_c = mean(smoking_age28mum_c, na.rm = TRUE)
  )

covariates_means_sens <- sensitivity_list_with_scores[[1]] %>%
  summarise(
    age_at_birth_mums_c = mean(age_at_birth_mums_c, na.rm = TRUE),
    familial_depressive_history_c = mean(familial_depressive_history_c, na.rm = TRUE),
    contextual_age28mum_c = mean(contextual_age28mum_c, na.rm = TRUE),
    depression_at_age28mum_c = mean(depression_at_age28mum_c, na.rm = TRUE),
    physical_activity_age28mum_c = mean(physical_activity_age28mum_c, na.rm = TRUE),
    smoking_age28mum_c = mean(smoking_age28mum_c, na.rm = TRUE)
  )

for (cov in names(covariates_means)) {
  pred_grid[[cov]] <- covariates_means[[cov]]
}

for (cov in names(covariates_means_sens)) {
  pred_grid_sens[[cov]] <- covariates_means_sens[[cov]]
}

# Step 5: Get coefficient estimates
coef_vals <- setNames(pooled_coefs$estimate, pooled_coefs$term)
coef_vals_sens <- setNames(pooled_coefs_sens$estimate, pooled_coefs_sens$term)

# Step 6: Calculate predicted values
pred_grid$predicted_depression <- with(pred_grid,
  coef_vals["(Intercept)"] +
    coef_vals["active_travel_age30mum_c"] * active_travel_age30mum_c +
    coef_vals["BuiltEnv_c"] * BuiltEnv_c +
    coef_vals["active_travel_age30mum_c:BuiltEnv_c"] * active_travel_age30mum_c * BuiltEnv_c +
    coef_vals["age_at_birth_mums_c"] * age_at_birth_mums_c +
    coef_vals["familial_depressive_history_c"] * familial_depressive_history_c +
    coef_vals["contextual_age28mum_c"] * contextual_age28mum_c +
    coef_vals["depression_at_age28mum_c"] * depression_at_age28mum_c +
    coef_vals["physical_activity_age28mum_c"] * physical_activity_age28mum_c +
    coef_vals["smoking_age28mum_c"] * smoking_age28mum_c
)

pred_grid_sens$predicted_depression <- with(pred_grid_sens,
  coef_vals_sens["(Intercept)"] +
    coef_vals_sens["active_travel_age30mum_c"] * active_travel_age30mum_c +
    coef_vals_sens["BuiltEnv_c"] * BuiltEnv_c +
    coef_vals_sens["active_travel_age30mum_c:BuiltEnv_c"] * active_travel_age30mum_c * BuiltEnv_c +
    coef_vals_sens["age_at_birth_mums_c"] * age_at_birth_mums_c +
    coef_vals_sens["familial_depressive_history_c"] * familial_depressive_history_c +
    coef_vals_sens["contextual_age28mum_c"] * contextual_age28mum_c +
    coef_vals_sens["depression_at_age28mum_c"] * depression_at_age28mum_c +
    coef_vals_sens["physical_activity_age28mum_c"] * physical_activity_age28mum_c +
    coef_vals_sens["smoking_age28mum_c"] * smoking_age28mum_c
)

# adjusted r squared
get_adj_r2 <- function(model_list) {
  r2_vals <- sapply(model_list$analyses, function(mod) {
    summary(mod)$adj.r.squared
  })
  mean(r2_vals)  # Rubin-style average 
}

adj_r2_mod1 <- get_adj_r2(moderation_model)
adj_r2_mod2 <- get_adj_r2(moderation_model2)

adj_r2_sens1 <- get_adj_r2(sensitivity_model)
adj_r2_sens2 <- get_adj_r2(sensitivity_model2)


# table formatting functions 
make_pool_table <- function(model, title = NULL) {
  
  label_df <- data.frame(
    term = c(
      "(Intercept)",
      "active_travel_age30mum_c",
      "BuiltEnv_c",
      "active_travel_age30mum_c:BuiltEnv_c",
      "age_at_birth_mums_c",
      "familial_depressive_history_c",
      "contextual_age28mum_c",
      "physical_activity_age28mum_c",
      "depression_at_age28mum_c",
      "smoking_age28mum_c"
    ),
    Predictor = c(
      "Intercept",
      "Active travel",
      "Built environment",
      "Active travel × built environment",
      "Age at enrolment",
      "Familial depressive history",
      "SES Risk Factors",
      "Physical activity",
      "Baseline depressive symptoms",
      "Smoking"
    ),
    stringsAsFactors = FALSE
  )
  
  # Mean adjusted R-squared across imputed models
  adj_r2 <- mean(sapply(model$analyses, function(mod) {
    summary(mod)$adj.r.squared
  }), na.rm = TRUE)
  
  tab <- summary(pool(model), conf.int = TRUE) |>
    left_join(label_df, by = "term") |>
    mutate(
      Predictor = ifelse(is.na(Predictor), term, Predictor),
      Estimate = sprintf("%.7f", estimate),
      SE = sprintf("%.7f", std.error),
      Statistic = sprintf("%.2f", statistic),
      df = sprintf("%.1f", df),
      `95% CI` = sprintf("[%.3f, %.3f]", `2.5 %`, `97.5 %`),
      `p-value` = ifelse(p.value < .001, "< .001", sprintf("%.5f", p.value)),
      sig = p.value < .05
    ) |>
    select(Predictor, Estimate, SE, Statistic, df, `95% CI`, `p-value`, sig)
  
  gt(tab) |>
    cols_hide(columns = sig) |>
    tab_style(
      style = cell_text(weight = "bold"),
      locations = cells_body(rows = sig)
    ) |>
    tab_header(title = title) |>
    tab_source_note(
      source_note = paste0("Adjusted R", html("&sup2;"), " = ", sprintf("%.3f", adj_r2))
    )
}

# descriptives prep 
descriptive_data <- imp_list_with_scores[[1]]

cont_vars <- c(
  "active_travel_age30mum",
  "BuiltEnv",
  "age_at_birth_mums",
  "depression_at_age28mum",
  "depression_at_age32mum",
  "physical_activity_age28mum",
  "age_at_travel_age30mum",
  "contextual_age28mum"
)


# -----------------------------
# Continuous descriptives table
# -----------------------------
cont_table <- descriptive_data |>
  summarise(across(all_of(cont_vars),
    list(
      n    = ~sum(!is.na(.x)),
      mean = ~mean(.x, na.rm = TRUE),
      sd   = ~sd(.x, na.rm = TRUE),
      min  = ~min(.x, na.rm = TRUE),
      max  = ~max(.x, na.rm = TRUE)
    ),
    .names = "{.col}_{.fn}"
  )) |>
  pivot_longer(
    everything(),
    names_to = c("Variable", ".value"),
    names_pattern = "^(.*)_(n|mean|sd|min|max)$"
  ) |>
  mutate(
    mean = round(mean, 3),
    sd   = round(sd, 3),
    min  = round(min, 3),
    max  = round(max, 3),
    Variable = recode(Variable,
      active_travel_age30mum = "Active travel behaviour",
      BuiltEnv = "Built environment factor",
      age_at_birth_mums = "Age at enrolment",
      age_at_travel_age30mum = "Age at active travel",
      depression_at_age28mum = "Depressive symptoms at enrolment",
      depression_at_age32mum = "Depressive symptoms at 4-year follow-up",
      physical_activity_age28mum = "Physical activity",
      contextual_age28mum = "SES risk factors"
    )
  )

# -----------------------------
# Categorical descriptives table
# -----------------------------
cat_vars <- c(
  "smoking_age28mum",
  "familial_depressive_history",
  "ethnicity_mum"
)

cat_data <- imp_list_with_scores[[1]]

cat_table <- bind_rows(
  tibble(
    Display = "Familial Depressive History",
    Percent = "",
    order = 1
  ),
  cat_data %>%
    count(familial_depressive_history) %>%
    mutate(
      Display = case_when(
        familial_depressive_history == 0 ~ "   None",
        familial_depressive_history == 1 ~ "   One parent",
        familial_depressive_history == 2 ~ "   Two parents",
        TRUE ~ paste0("   ", familial_depressive_history)
      ),
      Percent = paste0(n, " (", round(100 * n / sum(n), 1), "%)"),
      order = 2:4
    ) %>%
    select(Display, Percent, order),
  
  tibble(
    Display = "Smoking",
    Percent = "",
    order = 5
  ),
  cat_data %>%
    count(smoking_age28mum) %>%
    mutate(
      Display = case_when(
        smoking_age28mum == 0 ~ "   Never",
        smoking_age28mum == 1 ~ "   Until pregnancy",
        smoking_age28mum == 2 ~ "   During pregnancy",
        TRUE ~ paste0("   ", smoking_age28mum)
      ),
      Percent = paste0(n, " (", round(100 * n / sum(n), 1), "%)"),
      order = 6:8
    ) %>%
    select(Display, Percent, order),
  
  tibble(
    Display = "Ethnicity",
    Percent = "",
    order = 9
  ),
  cat_data %>%
    count(ethnicity_mum) %>%
    mutate(
      Display = case_when(
        ethnicity_mum == 1 ~ "   White",
        ethnicity_mum == 2 ~ "   Non-white",
        TRUE ~ paste0("   ", ethnicity_mum)
      ),
      Percent = paste0(n, " (", round(100 * n / sum(n), 1), "%)"),
      order = 10:11
    ) %>%
    select(Display, Percent, order)
) %>%
  arrange(order) %>%
  select(-order)

# correlations

corr_data <- imp_list_with_scores[[1]] %>%
  select(
    active_travel_age30mum,
    BuiltEnv,
    age_at_birth_mums,
    depression_at_age28mum,
    depression_at_age32mum,
    physical_activity_age28mum,
    smoking_age28mum,
    familial_depressive_history,
    contextual_age28mum,
    ethnicity_mum
  ) %>%
  rename(
    "Active Travel Behaviour" = active_travel_age30mum,
    "Built Environment Factor" = BuiltEnv,
    "Age at Enrolment" = age_at_birth_mums,
    "Depressive Symptoms (study enrolment)" = depression_at_age28mum,
    "Depression Symptoms (4-year follow-up)" = depression_at_age32mum,
    "Physical Activity" = physical_activity_age28mum,
    "Smoking" = smoking_age28mum,
    "Familial Depressive History" = familial_depressive_history,
    "SES Risk Factors" = contextual_age28mum,
    "Ethnicity" = ethnicity_mum
  )

corr_mat <- cor(corr_data, use = "pairwise.complete.obs")

# variables from first imputed dataset
df <- imp_list_with_scores[[1]]

# helper function
get_cor_test <- function(data, x, y) {
  test <- cor.test(data[[x]], data[[y]], use = "pairwise.complete.obs")
  data.frame(
    var1 = x,
    var2 = y,
    r = unname(test$estimate),
    p = test$p.value
  )
}

# run the specific correlations you want
cor_results <- dplyr::bind_rows(
  get_cor_test(df, "BuiltEnv", "depression_at_age28mum"),
  get_cor_test(df, "BuiltEnv", "depression_at_age32mum"),
  get_cor_test(df, "active_travel_age30mum", "BuiltEnv"),
  get_cor_test(df, "active_travel_age30mum", "depression_at_age28mum"),
  get_cor_test(df, "active_travel_age30mum", "depression_at_age32mum"),
  get_cor_test(df, "depression_at_age28mum", "depression_at_age32mum")
) %>%
  dplyr::mutate(
    r_round = round(r, 2),
    p_round = dplyr::case_when(
      p < .001 ~ "< .001",
      TRUE ~ sprintf("%.3f", p)
    )
  )


# Active travel category breakdown
travel_cat_table <- descriptive_data %>%
  mutate(
    active_travel_score_mum = case_when(
      active_travel_score_mum == 3 ~ "Active travel only",
      active_travel_score_mum == 2 ~ "Active travel + other modes",
      active_travel_score_mum == 1 ~ "Public transport/other only",
      active_travel_score_mum == 0 ~ "Car / none / not working",
      TRUE ~ NA_character_
    )
  ) %>%
  count(active_travel_score_mum) %>%
  mutate(
    Percent = paste0(n, " (", round(100 * n / sum(n), 1), "%)")
  ) %>%
  rename(Category = active_travel_score_mum)

# Journey time categories (to work)
jt1_table <- imp_list_with_scores[[1]] %>%
  count(journey_time1_mum) %>%
  mutate(
    Category = case_when(
      journey_time1_mum == 0 ~ "0 minutes",
      journey_time1_mum == 8 ~ "8 minutes",
      journey_time1_mum == 22 ~ "22 minutes",
      journey_time1_mum == 45 ~ "45 minutes",
      journey_time1_mum == 60 ~ "60 minutes"
    ),
    Percent = paste0(n, " (", round(100 * n / sum(n), 1), "%)")
  ) %>%
  select(Category, Percent)

# Journey time categories (from work)
jt2_table <- imp_list_with_scores[[1]] %>%
  count(journey_time2_mum) %>%
  mutate(
    Category = case_when(
      journey_time2_mum == 0 ~ "0 minutes",
      journey_time2_mum == 8 ~ "8 minutes",
      journey_time2_mum == 22 ~ "22 minutes",
      journey_time2_mum == 45 ~ "45 minutes",
      journey_time2_mum == 60 ~ "60 minutes"
    ),
    Percent = paste0(n, " (", round(100 * n / sum(n), 1), "%)")
  ) %>%
  select(Category, Percent)

# sensitivity descriptives prep 
# -----------------------------
# Sensitivity descriptives prep
# -----------------------------
sensitivity_descriptive_data <- sensitivity_list_with_scores[[1]]

# Continuous descriptives table
cont_table_sens <- sensitivity_descriptive_data |>
  summarise(across(all_of(cont_vars),
    list(
      n    = ~sum(!is.na(.x)),
      mean = ~mean(.x, na.rm = TRUE),
      sd   = ~sd(.x, na.rm = TRUE),
      min  = ~min(.x, na.rm = TRUE),
      max  = ~max(.x, na.rm = TRUE)
    ),
    .names = "{.col}_{.fn}"
  )) |>
  pivot_longer(
    everything(),
    names_to = c("Variable", ".value"),
    names_pattern = "^(.*)_(n|mean|sd|min|max)$"
  ) |>
  mutate(
    mean = round(mean, 3),
    sd   = round(sd, 3),
    min  = round(min, 3),
    max  = round(max, 3),
    Variable = recode(Variable,
      active_travel_age30mum = "Active travel behaviour",
      BuiltEnv = "Built environment factor",
      age_at_birth_mums = "Age at enrolment",
      depression_at_age28mum = "Depressive symptoms at enrolment",
      depression_at_age32mum = "Depressive symptoms at 4-year follow-up",
      physical_activity_age28mum = "Physical activity",
      contextual_age28mum = "SES risk factors"
    )
  )

# Categorical descriptives table
cat_table_sens <- bind_rows(
  tibble(
    Display = "Familial Depressive History",
    Percent = "",
    order = 1
  ),
  sensitivity_descriptive_data %>%
    count(familial_depressive_history) %>%
    mutate(
      Display = case_when(
        familial_depressive_history == 0 ~ "   None",
        familial_depressive_history == 1 ~ "   One parent",
        familial_depressive_history == 2 ~ "   Two parents",
        TRUE ~ paste0("   ", familial_depressive_history)
      ),
      Percent = paste0(n, " (", round(100 * n / sum(n), 1), "%)"),
      order = 2:4
    ) %>%
    select(Display, Percent, order),
  
  tibble(
    Display = "Smoking",
    Percent = "",
    order = 5
  ),
  sensitivity_descriptive_data %>%
    count(smoking_age28mum) %>%
    mutate(
      Display = case_when(
        smoking_age28mum == 0 ~ "   Never",
        smoking_age28mum == 1 ~ "   Until pregnancy",
        smoking_age28mum == 2 ~ "   During pregnancy",
        TRUE ~ paste0("   ", smoking_age28mum)
      ),
      Percent = paste0(n, " (", round(100 * n / sum(n), 1), "%)"),
      order = 6:8
    ) %>%
    select(Display, Percent, order),
  
  tibble(
    Display = "Ethnicity",
    Percent = "",
    order = 9
  ),
  sensitivity_descriptive_data %>%
    count(ethnicity_mum) %>%
    mutate(
      Display = case_when(
        ethnicity_mum == 1 ~ "   White",
        ethnicity_mum == 2 ~ "   Non-white",
        TRUE ~ paste0("   ", ethnicity_mum)
      ),
      Percent = paste0(n, " (", round(100 * n / sum(n), 1), "%)"),
      order = 10:11
    ) %>%
    select(Display, Percent, order)
) %>%
  arrange(order) %>%
  select(-order)

# Active travel category breakdown
travel_cat_table_sens <- sensitivity_descriptive_data %>%
  mutate(
    active_travel_score_mum = case_when(
      active_travel_score_mum == 3 ~ "Active travel only",
      active_travel_score_mum == 2 ~ "Active travel + other modes",
      active_travel_score_mum == 1 ~ "Public transport/other only",
      active_travel_score_mum == 0 ~ "Car / none / not working",
      TRUE ~ NA_character_
    )
  ) %>%
  count(active_travel_score_mum) %>%
  mutate(
    Percent = paste0(n, " (", round(100 * n / sum(n), 1), "%)")
  ) %>%
  rename(Category = active_travel_score_mum)

# Journey time categories
jt1_table_sens <- sensitivity_descriptive_data %>%
  count(journey_time1_mum) %>%
  mutate(
    Category = case_when(
      journey_time1_mum == 0 ~ "0 minutes",
      journey_time1_mum == 8 ~ "8 minutes",
      journey_time1_mum == 22 ~ "22 minutes",
      journey_time1_mum == 45 ~ "45 minutes",
      journey_time1_mum == 60 ~ "60 minutes"
    ),
    Percent = paste0(n, " (", round(100 * n / sum(n), 1), "%)")
  ) %>%
  select(Category, Percent)

jt2_table_sens <- sensitivity_descriptive_data %>%
  count(journey_time2_mum) %>%
  mutate(
    Category = case_when(
      journey_time2_mum == 0 ~ "0 minutes",
      journey_time2_mum == 8 ~ "8 minutes",
      journey_time2_mum == 22 ~ "22 minutes",
      journey_time2_mum == 45 ~ "45 minutes",
      journey_time2_mum == 60 ~ "60 minutes"
    ),
    Percent = paste0(n, " (", round(100 * n / sum(n), 1), "%)")
  ) %>%
  select(Category, Percent)

```

# Variable information

## Active Travel Behaviour
At a 2-year follow-up, mothers were asked, ‘How do you usually travel to work?’ with multiple-choiceresponses including ‘walk’, ‘public transport (bus/train)’, ‘cycle’, ‘car’, ‘work from home’ and ‘other (please describe)’. Active travel behaviours will be coded in the following order from lowest to highest active travel scores: (0) Work from home, don’t work, or by car only or car and public transport or other, (1) by public transport or other, (2) walking or cycling and another mode and (3) walking and/or cycling only. At the same time, mothers were also asked, ‘How long does it usually take to travel to work?’ with responses including ‘less than 15 minutes’, ‘15-29 minutes’, ‘30-59 minutes’ or ‘hour or more’. The same question was asked for journey times back from work. In order to make findings more translatable, we will take the midpoint of these times and round up to the nearest minute. For example, participants who responded with ‘less than 15 minutes’ will be given a journey time of 8 minutes, and participants who responded with ‘15-29 minutes’ will be given a journey time of 22 minutes. For the ‘hour or more’ category where no maximum is given, 60 minutes will be used instead. To better capture the overall dose of active travel exposure, we derived a composite measure by multiplying the ordinal active travel score by total commuting time. This approach integrates both the intensity of travel mode and duration of exposure, consistent with dose-based conceptualisations of physical activity (e.g., MET-minutes (Strath et al., 2013)), and allows differentiation between individuals with similar travel modes but differing journey lengths. 

## Physical Activity
At study enrolment, mothers were asked ‘How much do you do the following at present?’ followed by ‘jogging’, ‘aerobics’, ‘ante natal exercise’, ‘keep fit’, ‘yoga’, ‘squash’, ‘tennis/badminton’, ‘swimming’, ‘brisk walking’, ‘weight training’, ‘cycling’ ‘other exercise’. Mothers could then respond with, ‘Never’, ‘Less than one hour per week’, ‘2-6 hours per week’, and ‘more than 7 hours per week’. As described by Liu and colleagues (2011), scores were then weighted according to average metabolic equivalent scores meaning they represented the weekly total energy expenditure from activities reported. Higher scores represent greater total energy expenditure from reported physical activities. Controlling for general levels of physical activity is important because it associates with depressive symptoms and active travel behaviour (Kroesen & De Vos, 2020; Wanjau et al., 2023). 


# Descriptives

```{r cars, echo=FALSE, warning=FALSE}

gt(cont_table) |>
  cols_label(
    Variable = "Variable",
    n = "N",
    mean = "Mean",
    sd = "SD",
    min = "Min",
    max = "Max"
  ) |>
  tab_header(title = "Continuous variables")

gt(cat_table) |>
  cols_label(
    Display = "",
    Percent = ""
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      rows = Percent == ""
    )
  ) |>
  cols_align(
    align = "left",
    columns = Display
  ) |>
  cols_align(
    align = "left",
    columns = Percent
  ) |>
  tab_header(title = "Categorical variables")


gt(travel_cat_table) %>%
  cols_label(
    Category = "Travel behaviour category",
    n = "N",
    Percent = "Percent"
  ) %>%
  tab_header(title = "Active travel behaviour categories")

gt(jt1_table) %>%
  tab_header(title = "Journey time categories (outward journey")

gt(jt2_table) %>%
  tab_header(title = "Journey time categories (return journey)")

ggcorrplot(
  corr_mat,
  type = "lower",
  lab = TRUE,
  lab_size = 3,
  show.diag = TRUE
)

# Scatterplot: built environment with active travel
ggplot(descriptive_data,
       aes(x = BuiltEnv,
           y = active_travel_age30mum)) +

  geom_point(
    alpha = 0.3,
    size = 0.3,
    colour = "orchid4"
  ) +

  geom_smooth(
    method = "lm",
    se = TRUE,
    linewidth = 1.0,
    colour = "black",
    fill = "grey50"
  ) +

  labs(
    x = "Built environment factor",
    y = "Active travel behaviour"
  ) +

  theme_classic(base_size = 14) +

  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(colour = "black"),
    plot.title = element_blank()
  )

# Scatterplot: active travel with depressive symptoms
ggplot(descriptive_data,
       aes(x = active_travel_age30mum,
           y = depression_at_age32mum)) +

  geom_point(
    alpha = 0.3,
    size = 0.3,
    colour = "orchid4"
  ) +

  geom_smooth(
    method = "lm",
    se = TRUE,
    linewidth = 1.0,
    colour = "black",
    fill = "grey50"
  ) +

  labs(
    x = "Active travel behaviour",
    y = "Depressive symptoms (4-year follow-up)"
  ) +

  theme_classic(base_size = 14) +

  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(colour = "black"),
    plot.title = element_blank()
  )

# Scatterplot: built environment with depressive symptoms
ggplot(descriptive_data,
       aes(x = BuiltEnv,
           y = depression_at_age32mum)) +

  geom_point(
    alpha = 0.3,
    size = 0.3,
    colour = "orchid4"
  ) +

  geom_smooth(
    method = "lm",
    se = TRUE,
    linewidth = 1.0,
    colour = "black",
    fill = "grey50"
  ) +

  labs(
    x = "Built Environment Factor",
    y = "Depressive symptoms (4-year follow-up)"
  ) +

  theme_classic(base_size = 14) +

  theme(
    axis.title = element_text(face = "bold"),
    axis.text = element_text(colour = "black"),
    plot.title = element_blank()
  )


# Sensitivity descriptives

gt(cont_table_sens) |>
  cols_label(
    Variable = "Variable",
    n = "N",
    mean = "Mean",
    sd = "SD",
    min = "Min",
    max = "Max"
  ) |>
  tab_header(title = "Sensitivity sample: Continuous variables")

gt(cat_table_sens) |>
  cols_label(
    Display = "",
    Percent = ""
  ) |>
  tab_style(
    style = cell_text(weight = "bold"),
    locations = cells_body(
      rows = Percent == ""
    )
  ) |>
  cols_align(
    align = "left",
    columns = Display
  ) |>
  cols_align(
    align = "left",
    columns = Percent
  ) |>
  tab_header(title = "Sensitivity sample: Categorical variables")

gt(travel_cat_table_sens) %>%
  cols_label(
    Category = "Travel behaviour category",
    n = "N",
    Percent = "Percent"
  ) %>%
  tab_header(title = "Sensitivity sample: Active travel behaviour categories")

gt(jt1_table_sens) %>%
  tab_header(title = "Sensitivity sample: Journey time categories (outward journey)")

gt(jt2_table_sens) %>%
  tab_header(title = "Sensitivity sample: Journey time categories (return journey)")

```

# Results

```{r pressure, echo=FALSE}

make_pool_table(moderation_model, "Moderation Model Adjusted")

make_pool_table(moderation_model2, "Moderation Model Unadjusted")

make_pool_table(moderation_model_std, "Standardised Moderation Model Adjusted")
make_pool_table(moderation_model2_std, "Standardised Moderation Model Unadjusted")

```


```{r plots, echo=FALSE}

ggplot(
  pred_grid,
  aes(
    x = active_travel_age30mum_c,
    y = predicted_depression,
    color = factor(BuiltEnv_c)
  )
) +
  geom_line(linewidth = 1) +

  scale_color_manual(
    name = "Built environment",
    labels = c(
      "Low (-1 SD)",
      "Mean (0)",
      "High (+1 SD)"
    ),
    values = c(
      "plum2",
      "orchid4",
      "purple4"
    )
  ) +

  labs(
    x = "Active travel behaviour",
    y = "Predicted depressive symptoms"
  ) +

  theme_classic(base_size = 14) +

  theme(
    axis.title = element_text(face = "bold", colour = "black"),
    axis.text = element_text(colour = "black"),
    axis.line = element_line(colour = "black"),
    axis.ticks = element_line(colour = "black"),
    legend.title = element_text(face = "bold"),
    legend.text = element_text(colour = "black"),
    plot.title = element_blank()
  )

```

# Sensitivity analysis (complete data only for active travel)

```{r sensitivity, echo=FALSE}

make_pool_table(sensitivity_model, "Sensitivity Model Adjusted")

make_pool_table(sensitivity_model2, "Sensitivity Model Unadjusted")

make_pool_table(sensitivity_model_std, "Standardised Sensitivity Model Adjusted")
make_pool_table(sensitivity_model2_std, "Standardised Sensitivity Model Unadjusted")

```


```{r sensitivityplots, echo=FALSE}

ggplot(pred_grid_sens, aes(x = active_travel_age30mum_c, y = predicted_depression, color = factor(BuiltEnv_c))) +
  geom_line(linewidth = 1) +
  scale_color_manual(name = "BuiltEnv Level",
                     labels = c("Low (-1 SD)", "Mean (0)", "High (+1 SD)"),
                     values = c("blue", "black", "red")) +
  labs(
    x = "Active Travel",
    y = "Depression at Age 32",
    title = "Sensitivity: Depression by Active Travel and Built Environment Levels"
  ) +
  theme_minimal()
```

```{r casecontrol, echo=FALSE}
# ==============================================================================
# CASE-CONTROL STYLE ANALYSIS
# Active travel coded as binary outcome: 0 = no active travel, 1 = any active travel
# ==============================================================================

# Create binary active travel variable
case_control_data <- descriptive_data %>%
  mutate(
    active_travel_binary = case_when(
      active_travel_score_mum %in% c(0, 1) ~ 0,
      active_travel_score_mum %in% c(2, 3) ~ 1,
      TRUE ~ NA_real_
    ),
    active_travel_binary = factor(
      active_travel_binary,
      levels = c(0, 1),
      labels = c("No active travel", "Any active travel")
    )
  )

# Standardised variables for case-control regression
case_control_data <- case_control_data %>%
  mutate(
    depression_at_age32mum_z = as.numeric(scale(depression_at_age32mum)),
    BuiltEnv_z = as.numeric(scale(BuiltEnv)),
    age_at_birth_mums_z = as.numeric(scale(age_at_birth_mums)),
    contextual_age28mum_z = as.numeric(scale(contextual_age28mum)),
    physical_activity_age28mum_z = as.numeric(scale(physical_activity_age28mum)),
    depression_at_age28mum_z = as.numeric(scale(depression_at_age28mum))
  )

# Check numbers in each group
active_binary_table <- case_control_data %>%
  count(active_travel_binary) %>%
  mutate(
    Percent = paste0(round(100 * n / sum(n), 1), "%")
  )

gt(active_binary_table) %>%
  cols_label(
    active_travel_binary = "Active travel group",
    n = "N",
    Percent = "Percent"
  ) %>%
  tab_header(title = "Binary active travel groups")


# ------------------------------------------------------------------------------
# Model 1: Does built environment predict active travel group?
# Logistic regression
# ------------------------------------------------------------------------------

active_travel_binary_model <- glm(
  active_travel_binary ~ BuiltEnv,
  data = case_control_data,
  family = binomial
)

summary(active_travel_binary_model)


# Adjusted model
active_travel_binary_model_adj <- glm(
  active_travel_binary ~ BuiltEnv +
    age_at_birth_mums +
    familial_depressive_history +
    contextual_age28mum +
    physical_activity_age28mum +
    depression_at_age28mum +
    smoking_age28mum,
  data = case_control_data,
  family = binomial
)

summary(active_travel_binary_model_adj)

# ------------------------------------------------------------------------------
# Standardised Model 2:
# Is active travel group associated with depression outcome?
# ------------------------------------------------------------------------------

# Unadjusted model
depression_binary_model_std <- lm(
  depression_at_age32mum_z ~ active_travel_binary,
  data = case_control_data
)

summary(depression_binary_model_std)


# Adjusted model
depression_binary_model_adj_std <- lm(
  depression_at_age32mum_z ~ active_travel_binary * BuiltEnv_z +
    age_at_birth_mums_z +
    familial_depressive_history +
    contextual_age28mum_z +
    physical_activity_age28mum_z +
    depression_at_age28mum_z +
    smoking_age28mum,
  data = case_control_data
)

summary(depression_binary_model_adj_std)


# Regression table
depression_binary_table_std <- broom::tidy(
  depression_binary_model_adj_std,
  conf.int = TRUE
) %>%
  mutate(
    term = recode(
      term,
      "(Intercept)" = "Intercept",
      "active_travel_binaryAny active travel" = "Active travel group",
      "BuiltEnv_z" = "Built environment",
      "age_at_birth_mums_z" = "Age at enrolment",
      "familial_depressive_history" = "Familial depressive history",
      "contextual_age28mum_z" = "SES risk factors",
      "physical_activity_age28mum_z" = "Physical activity",
      "depression_at_age28mum_z" = "Baseline depressive symptoms",
      "smoking_age28mum" = "Smoking",
      "active_travel_binaryAny active travel:BuiltEnv_z" =
        "Active travel group × built environment"
    ),
    Estimate = round(estimate, 3),
    SE = round(std.error, 3),
    CI = paste0(
      "[",
      round(conf.low, 3),
      ", ",
      round(conf.high, 3),
      "]"
    ),
    p_value = case_when(
      p.value < .001 ~ "< .001",
      TRUE ~ sprintf("%.3f", p.value)
    )
  ) %>%
  select(term, Estimate, SE, CI, p_value)


gt(depression_binary_table_std) %>%
  cols_label(
    term = "Predictor",
    Estimate = "Standardised estimate",
    SE = "SE",
    CI = "95% CI",
    p_value = "p-value"
  ) %>%
  tab_header(
    title = "Standardised adjusted linear regression: active travel group predicting depression"
  )


# Odds ratios with 95% confidence intervals
active_travel_or_table <- broom::tidy(
  active_travel_binary_model_adj,
  conf.int = TRUE,
  exponentiate = TRUE
) %>%
  mutate(
    OR = round(estimate, 3),
    CI = paste0("[", round(conf.low, 3), ", ", round(conf.high, 3), "]"),
    p_value = case_when(
      p.value < .001 ~ "< .001",
      TRUE ~ sprintf("%.3f", p.value)
    )
  ) %>%
  select(term, OR, CI, p_value)

gt(active_travel_or_table) %>%
  cols_label(
    term = "Predictor",
    OR = "Odds ratio",
    CI = "95% CI",
    p_value = "p-value"
  ) %>%
  tab_header(title = "Adjusted logistic regression: built environment predicting active travel group")


# ------------------------------------------------------------------------------
# Model 2: Is active travel group associated with depression outcome?
# Linear regression
# ------------------------------------------------------------------------------

depression_binary_model <- lm(
  depression_at_age32mum ~ active_travel_binary,
  data = case_control_data
)

summary(depression_binary_model)


# Adjusted model
depression_binary_model_adj <- lm(
  depression_at_age32mum ~ active_travel_binary * BuiltEnv +
    age_at_birth_mums +
    familial_depressive_history +
    contextual_age28mum +
    physical_activity_age28mum +
    depression_at_age28mum +
    smoking_age28mum,
  data = case_control_data
)

summary(depression_binary_model_adj)


# Regression table
depression_binary_table <- broom::tidy(
  depression_binary_model_adj,
  conf.int = TRUE
) %>%
  mutate(
    Estimate = round(estimate, 3),
    SE = round(std.error, 3),
    CI = paste0("[", round(conf.low, 3), ", ", round(conf.high, 3), "]"),
    p_value = case_when(
      p.value < .001 ~ "< .001",
      TRUE ~ sprintf("%.3f", p.value)
    )
  ) %>%
  select(term, Estimate, SE, CI, p_value)

gt(depression_binary_table) %>%
  cols_label(
    term = "Predictor",
    Estimate = "Estimate",
    SE = "SE",
    CI = "95% CI",
    p_value = "p-value"
  ) %>%
  tab_header(title = "Adjusted linear regression: active travel group predicting depression")


# ------------------------------------------------------------------------------
# Plot 1: Built environment by active travel group
# ------------------------------------------------------------------------------

ggplot(case_control_data,
       aes(x = active_travel_binary,
           y = BuiltEnv,
           fill = active_travel_binary)) +
  geom_boxplot(alpha = 0.7, outlier.alpha = 0.4) +
  labs(
    title = "Built environment scores by active travel group",
    x = "Active travel group",
    y = "Built environment factor score",
    fill = "Active travel group"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold")
  )


# ------------------------------------------------------------------------------
# Plot 2: Depression outcome by active travel group
# ------------------------------------------------------------------------------

ggplot(case_control_data,
       aes(x = active_travel_binary,
           y = depression_at_age32mum,
           fill = active_travel_binary)) +
  geom_boxplot(alpha = 0.7, outlier.alpha = 0.4) +
  labs(
    title = "Depressive symptoms by active travel group",
    x = "Active travel group",
    y = "Depressive symptoms at 4-year follow-up",
    fill = "Active travel group"
  ) +
  theme_minimal(base_size = 14) +
  theme(
    legend.position = "none",
    plot.title = element_text(face = "bold")
  )

# ============================================================
# CORRELATIONS  WITH INDIVIDUAL BUILT ENVIRONMENT INDICATORS
# ============================================================

# ============================================================
# CORRELATION TABLE: BE indicators × Active travel & Depression (4-year FU)
# ============================================================

df <- imp_list_with_scores[[1]]

be_vars <- c(
  "building_density_age28mum",
  "connectivity_density_age28mum",
  "facility_richness_age28mum",
  "greenspace_age28mum",
  "pop_density_age28mum",
  "walkability_age28mum"
)

# Helper function (returns numeric p-values)
get_cor <- function(data, x, y) {
  test <- cor.test(data[[x]], data[[y]], use = "pairwise.complete.obs")
  tibble(
    BE_variable = x,
    Outcome = y,
    r = round(test$estimate, 3),
    p = test$p.value   # numeric here
  )
}

# Run correlations for each BE variable with both outcomes
cor_table <- purrr::map_df(be_vars, ~{
  bind_rows(
    get_cor(df, .x, "active_travel_age30mum"),
    get_cor(df, .x, "depression_at_age32mum")
  )
})

# Now safely format p-values as character
cor_table <- cor_table %>%
  mutate(
    p = ifelse(p < .001, "< .001", sprintf("%.3f", p)),
    Outcome = recode(Outcome,
      "active_travel_age30mum" = "Active travel behaviour",
      "depression_at_age32mum" = "Depressive symptoms (4-year follow-up)"
    ),
    BE_variable = recode(BE_variable,
      "building_density_age28mum" = "Building density",
      "connectivity_density_age28mum" = "Connectivity density",
      "facility_richness_age28mum" = "Facility richness",
      "greenspace_age28mum" = "Green space",
      "pop_density_age28mum" = "Population density",
      "walkability_age28mum" = "Walkability"
    )
  )

# Display table
gt(cor_table) %>%
  tab_header(title = "Correlations Between Built Environment Indicators and Active Travel Behaviour (2-year follow-up) and Depressive Symptoms (4-year follow-up)") %>%
  cols_label(
    BE_variable = "Built Environment Indicator",
    Outcome = "Outcome",
    r = "Correlation (r)",
    p = "p-value"
  )

```

```{r interactionplots, echo=FALSE}

# Interaction plot new
# ============================================================
# INTERACTION PLOT
# Active travel moderates the association between
# built environment and depressive symptoms
# ============================================================


# ------------------------------------------------------------
# 1. Built environment across observed range
# ------------------------------------------------------------

built_env_mean <- mean(
  imp_list_with_scores[[1]]$BuiltEnv,
  na.rm = TRUE
)

built_env_raw_vals <- seq(
  from = min(
    imp_list_with_scores[[1]]$BuiltEnv,
    na.rm = TRUE
  ),
  to = max(
    imp_list_with_scores[[1]]$BuiltEnv,
    na.rm = TRUE
  ),
  length.out = 100
)

# Centre for model prediction
built_env_vals <-
  built_env_raw_vals - built_env_mean


# ------------------------------------------------------------
# 2. Active travel at low, mean and high levels
# ------------------------------------------------------------

active_travel_sd <- sd(
  imp_list_with_scores[[1]]$active_travel_age30mum_c,
  na.rm = TRUE
)

active_travel_vals <- c(
  -active_travel_sd,
  0,
  active_travel_sd
)


# ------------------------------------------------------------
# 3. Create prediction grid
# ------------------------------------------------------------

pred_grid <- expand.grid(
  BuiltEnv_c = built_env_vals,
  active_travel_age30mum_c = active_travel_vals
)


# ------------------------------------------------------------
# 4. Hold covariates at their means
# ------------------------------------------------------------

covariates_means <- imp_list_with_scores[[1]] %>%
  summarise(
    age_at_birth_mums_c =
      mean(age_at_birth_mums_c, na.rm = TRUE),

    familial_depressive_history_c =
      mean(familial_depressive_history_c, na.rm = TRUE),

    contextual_age28mum_c =
      mean(contextual_age28mum_c, na.rm = TRUE),

    depression_at_age28mum_c =
      mean(depression_at_age28mum_c, na.rm = TRUE),

    physical_activity_age28mum_c =
      mean(physical_activity_age28mum_c, na.rm = TRUE),

    smoking_age28mum_c =
      mean(smoking_age28mum_c, na.rm = TRUE)
  )

for (cov in names(covariates_means)) {
  pred_grid[[cov]] <- covariates_means[[cov]]
}


# ------------------------------------------------------------
# 5. Predictions from each imputed model
# ------------------------------------------------------------

predictions <- lapply(
  moderation_model$analyses,
  function(mod) {

    p <- predict(
      mod,
      newdata = pred_grid,
      se.fit = TRUE
    )

    data.frame(
      fit = as.numeric(p$fit),
      se = as.numeric(p$se.fit)
    )
  }
)


# ------------------------------------------------------------
# 6. Pool predictions across imputations
# ------------------------------------------------------------

m <- length(predictions)

pred_mat <- do.call(
  cbind,
  lapply(predictions, `[[`, "fit")
)

var_mat <- do.call(
  cbind,
  lapply(
    predictions,
    function(x) x$se^2
  )
)

# Pooled predicted depression
pred_grid$predicted_depression <-
  rowMeans(pred_mat)

# Within-imputation variance
within_var <-
  rowMeans(var_mat)

# Between-imputation variance
between_var <-
  apply(pred_mat, 1, var)

# Rubin's rules total variance
total_var <-
  within_var +
  (1 + 1 / m) * between_var

# Pooled SE
pred_grid$se <-
  sqrt(total_var)

# 95% confidence intervals
pred_grid$lower <-
  pred_grid$predicted_depression -
  1.96 * pred_grid$se

pred_grid$upper <-
  pred_grid$predicted_depression +
  1.96 * pred_grid$se


# ------------------------------------------------------------
# 7. Put built environment back on original scale
# ------------------------------------------------------------

pred_grid$BuiltEnv_plot <-
  pred_grid$BuiltEnv_c +
  built_env_mean


# ------------------------------------------------------------
# 8. Label active travel levels
# ------------------------------------------------------------

pred_grid$active_travel_level <- factor(
  pred_grid$active_travel_age30mum_c,
  levels = c(
    -active_travel_sd,
    0,
    active_travel_sd
  ),
  labels = c(
    "Low (-1 SD)",
    "Mean",
    "High (+1 SD)"
  )
)


# ------------------------------------------------------------
# 9. Plot
# ------------------------------------------------------------

ggplot(
  pred_grid,
  aes(
    x = BuiltEnv_plot,
    y = predicted_depression,
    colour = active_travel_level,
    fill = active_travel_level
  )
) +

  geom_ribbon(
    aes(
      ymin = lower,
      ymax = upper
    ),
    alpha = 0.08,
    colour = NA
  ) +

  geom_point(
    data = descriptive_data,
    aes(
      x = BuiltEnv,
      y = depression_at_age32mum
    ),
    inherit.aes = FALSE,
    alpha = 0.2,
    size = 0.5,
    colour = "grey40"
  ) +

  geom_line(
    linewidth = 1
  ) +

  scale_color_manual(
    name = "Active travel",
    values = c(
      "plum2",
      "orchid4",
      "purple4"
    )
  ) +

  scale_fill_manual(
    name = "Active travel",
    values = c(
      "plum2",
      "orchid4",
      "purple4"
    )
  ) +

  labs(
    x = "Built environment",
    y = "Predicted depressive symptoms"
  ) +

  theme_classic(base_size = 14) +

  theme(
    axis.title =
      element_text(face = "bold", colour = "black"),

    axis.text =
      element_text(colour = "black"),

    axis.line =
      element_line(colour = "black"),

    axis.ticks =
      element_line(colour = "black"),

    legend.title =
      element_text(face = "bold"),

    legend.text =
      element_text(colour = "black"),

    plot.title =
      element_blank()
  )

ggplot(
  pred_grid,
  aes(
    x = BuiltEnv_plot,
    y = predicted_depression,
    colour = active_travel_level,
    fill = active_travel_level
  )
) +

  geom_ribbon(
    aes(
      ymin = lower,
      ymax = upper
    ),
    alpha = 0.08,
    colour = NA
  ) +

  geom_point(
    data = descriptive_data,
    aes(
      x = BuiltEnv,
      y = depression_at_age32mum
    ),
    inherit.aes = FALSE,
    alpha = 0.2,
    size = 0.5,
    colour = "grey40"
  ) +

  geom_line(
    linewidth = 1
  ) +

  scale_color_manual(
    name = "Active travel",
    values = c(
      "plum2",
      "orchid4",
      "purple4"
    )
  ) +

  scale_fill_manual(
    name = "Active travel",
    values = c(
      "plum2",
      "orchid4",
      "purple4"
    )
  ) +

  labs(
    x = "Built environment",
    y = "Predicted depressive symptoms"
  ) +
  
   coord_cartesian(
    xlim = c(-1, 1),
    ylim = c(4, 8)
  ) +

  theme_classic(base_size = 14) +

  theme(
    axis.title =
      element_text(face = "bold", colour = "black"),

    axis.text =
      element_text(colour = "black"),

    axis.line =
      element_line(colour = "black"),

    axis.ticks =
      element_line(colour = "black"),

    legend.title =
      element_text(face = "bold"),

    legend.text =
      element_text(colour = "black"),

    plot.title =
      element_blank() 
  
  )
```
